Fast time-domain electromagnetic modelling in the frequency domain

### 2020-09-21 ManuscriptTime.tex
Correct NRMSD formula
start revision

\documentclass[
%     paper,
    manuscript,
%     twocolumn,
%     twoside,
%     revised,
  ]{geophysics}

@@

The results are shown in Figure~\ref{fig:3d-result}: In (a) the 1D background
responses and the relative error using the semi-analytical result obtained from
\empymod, and in (b) the responses including the target.
%
\plot{3d-result}{width=\textwidth}{
  Responses for the model outlined in Figure~\ref{fig:3d-model} using \simpeg
  and \emg3d, and for the layered background also \empymod. In the lower plot
  of (a) the relative error (\%) in comparison to \empymod is shown, and in (b)
  the normalized difference (\%) between the two 3D codes. The results of these
  plots are clipped for values smaller than 0.1\,\% and bigger than 10\,\%.
}
%
The background comparison shows that both 3D codes do an acceptable job having
a relative error of a few percents at most; the result for \emg3d seems to be
better at early times. We cannot compare the errors for the response that
includes the target for lack of an analytical solution. The background model
from \empymod is only included to show that there is a significant response
from the target. We therefore show the normalized difference (ND) between the
two 3D codes as a percentage, where $\mr{ND}=
50|(\simpeg-\emg3d)/(\simpeg+\emg3d)|$. The ND between the two codes is below
1\,\% everywhere except for early times.

>>>>

\documentclass[
%     paper,
    manuscript,
%     twocolumn,
%     twoside,
    revised,
  ]{geophysics}

@@

The results are shown in Figure~\ref{fig:3d-result}: In (a) the 1D background
responses and the relative error using the semi-analytical result obtained from
\empymod, and in (b) the responses including the target.
%
\plot{3d-result}{width=\textwidth}{
  Responses for the model outlined in Figure~\ref{fig:3d-model} using \simpeg
  and \emg3d, and for the layered background also \empymod. In the lower plot
  of (a) the relative error (\%) in comparison to \empymod is shown, and in (b)
  the normalized difference (\%) between the two 3D codes. The results of these
  plots are clipped for values smaller than 0.1\,\% and bigger than 10\,\%.
}
%
The background comparison shows that both 3D codes do an acceptable job having
a relative error of a few percents at most; the result for \emg3d seems to be
better at early times. We cannot compare the errors for the response that
includes the target for lack of an analytical solution. The background model
from \empymod is only included to show that there is a significant response
from the target. We therefore show the normalized difference (ND) between the
two 3D codes as a percentage, where
\old{$\mr{ND}= 50|(\simpeg-\emg3d)/(\simpeg+\emg3d)|$.}
\new{$\mr{ND}= 200|\simpeg-\emg3d|/(|\simpeg|+|\emg3d|)$.}
The ND between the two codes is below 1\,\% everywhere except for early times.
